---
title: "hw6"
author: "Yu Si"
date: "12/4/2021"
output: github_document
---

## Set up

```{r}
library(tidyverse)
library(modelr)
library(mgcv)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Problem 1


```{r}
#Data clean
birthweight_df = read_csv("birthweight.csv")

birthweight_df= 
  birthweight_df %>% 
    drop_na() %>% 
    mutate(
      babysex = fct_recode(factor(babysex), male = "1", female = "2"),
      frace = fct_recode(factor(frace), White = "1", Black = "2", Asian = "3", Puerto_Rican = "4", Other = "8"),
      malform = fct_recode(factor(malform), absent = "0", present = "1"),
      mrace = fct_recode(factor(mrace), White = "1", Black = "2", Asian = "3", Puerto_Rican = "4")
    )
```

There is a sense that baby's head circumference at birth is positively correlated to baby's birth weight and at the genetic level,mother's race plays a important role in baby's birth weight. From my point of view, the child's birthweight should be associated with baby's sex, baby's head circumference at birth, baby's length at birth, gestational age, mother's age at menarche, mother's race, father's race, and mother's weight gain during pregnancy. 

Let's explore if the categorical variables I listed above have some influence on the child's birth weight!

```{r}
birthweight_df %>% 
  select(bwt, babysex, frace, mrace) %>% 
  pivot_longer(
    cols = -bwt,
    names_to = "category",
    values_to = "levels"
  ) %>% 
  ggplot(aes(y = bwt, x = levels)) +
  geom_boxplot() +
  facet_wrap(. ~ category, scale = "free") +
  labs(
    y = "birth weight",
    title = "Distribution of Birthweight According to Different Categorical Variables"
  )
```

It seems that all of them will affect child's birthweight. 
Then, let's take a look at continuous variables

```{r}
birthweight_df %>% 
  select(bwt, bhead, blength, gaweeks, menarche, wtgain) %>% 
  pivot_longer(
    cols = -bwt, 
    names_to = "variables",
    values_to = "values"
  ) %>% 
  ggplot(aes(x = values, y = bwt)) +
  geom_point(alpha = .2) +
  facet_wrap(. ~ variables, scales = "free")+
  labs(
    y = "birth weight",
    title = "Distribution of Birthweight According to Different Continuous Variables"
  )
```

Based on the analysis, the age of mother at menarche does not have a significant impact on birthweight, which we will remove that variable in the model.

Here is the model:

```{r}
my_model = lm(bwt ~ bhead + blength + gaweeks + wtgain + babysex + frace + mrace, data = birthweight_df)
```

#Residuals in our model

```{r}
birthweight_df %>% 
  modelr::add_residuals(my_model) %>% 
  modelr::add_predictions(my_model) %>% 
  ggplot(aes(x = pred, y = resid)) +
  geom_point(alpha = .3) +
  labs(
    title = "Scatterplot for Residuals Against Fitted Values",
    x = "Predicted Birthweight",
    y = "Residual"
  )
```

compare with the other 2 model provided

```{r}
model1 = lm(bwt ~ blength + gaweeks, data = birthweight_df)
model2 = lm(bwt ~ bhead + babysex + blength + bhead * babysex + bhead * blength + babysex * blength + babysex * blength * bhead, data = birthweight_df)
```

Test the model fit

```{r}
set.seed(2)
cv_df = 
  crossv_mc(birthweight_df, 100) %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble)
  )

cv_df = 
  cv_df %>% 
  mutate(
    my_model = map(.x = train, ~ lm(bwt ~ bhead + blength + gaweeks + wtgain + babysex + frace + mrace, data = .x)),
    model1 = map(.x = train, ~lm(bwt ~ blength + gaweeks, data = .x)),
    model2 = map(.x = train, ~lm(bwt ~ bhead + babysex + blength + bhead * babysex + bhead * blength + babysex * blength + babysex * blength * bhead, data = .x))
    )%>% 
  mutate(
    rmse_my_model = map2_dbl(.x = my_model, .y = test, ~rmse(model = .x, data = .y)),
    rmse_model1 = map2_dbl(.x = model1, .y = test, ~rmse(model = .x, data = .y)),
    rmse_model2 = map2_dbl(.x = model2, .y = test, ~rmse(model = .x, data = .y))
  )

cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model",
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  ggplot(aes(x = model, y = rmse)) +
  geom_boxplot()
  

```

The plot above compared the prediction error of three models. The model using baby's length at birth has the highest average rmse compared to other two models, indicating a worse fitting of this model. The model I provided seems to have the smallest rmse among the three models which means it predicts the child's birth weight better than other two models provided.

## Problem 2

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```


```{r}
set.seed(1)
boot_straps = 
  weather_df %>% 
  modelr::bootstrap(n = 5000) %>% 
  mutate(
    model = map(strap, ~lm(tmax~tmin, data = .x)),
    glance = map(model, broom::glance),
    results = map(model, broom::tidy)
  ) %>% 
  unnest(glance) %>% 
  select(.id, r.squared, results) %>% 
  unnest(results) %>%
  mutate(
    term=str_replace(term,"\\(Intercept\\)","Intercept")
  ) %>% 
  pivot_wider(
    names_from = term,
    values_from = estimate
  ) %>% 
 group_by(.id) %>% 
  summarise(intercept = max(Intercept, na.rm = TRUE),
            tmin = max(tmin, na.rm = TRUE),
            r.squared = mean(r.squared)) %>% 
  mutate(
    result = log(intercept*tmin)
  )
boot_straps %>% 
  ggplot(aes(x = r.squared)) + geom_density()+
  labs(title = 'distribution of r_squared')
  
boot_straps %>% 
  ggplot(aes(x = r.squared)) + geom_density()+
  labs(title = 'distribution of log(beta0*beta1)')
```

Both r_squared and log(beta0*beta1) follows normal distribution, which align with central limit theorem.


```{r}
boot_straps %>% 
  summarize(
    r_squared_ci_lower = quantile(r.squared, 0.025), 
    r_squared_ci_upper = quantile(r.squared, 0.975),
    result_ci_lower = quantile(result, 0.025), 
    result_ci_upper = quantile(result, 0.975)) %>% 
  knitr::kable(caption = '95% CIs')
```


